\( \tool \): JavaScript IR-based Semantics Extraction Toolchain

### 2020-04-15 ase20/overview.tex
Revised Sec. 2

In this section, we introduce the overall structure of \( \tool \) depicted in
Figure~\ref{fig:overview}.  Compared to the existing approaches shown in
Figure~\ref{fig:existing}, our tool automatically synthesizes {\sf JavaScript
Parser} and {\sf AST-\( \ires \) Translator} directly from ECMAScript. The
motivation of this work is twofold: 1) ECMAScript is written in a well-organized
style, and 2) the writing style is converged since ES7 in 2016.

We explain how \( \tool \) utilize such common patterns in the writing style to
synthesize two modules with an example.  After {\sf Spec Extractor} extract
syntax and semantics in JSON format, our tool consists consists of two parts for
\textit{syntax} and \textit{semantics}.

>>>>

In this section, we introduce the overall structure of \( \tool \) depicted in
Figure~\ref{fig:overview}.  Compared to the existing approaches shown in
Figure~\ref{fig:existing}, our tool automatically synthesizes {\sf JavaScript
Parser} and {\sf AST-\( \ires \) Translator} directly from ECMAScript. The
motivation of this work is twofold: 1) ECMAScript is written in a well-organized
style, and 2) the writing style is converged since ES7 in 2016.
We explain how \( \tool \) utilizes such common patterns in the writing style to
synthesize {\sf JavaScript Parser} and {\sf AST-\( \ires \) Translator}
using the syntax and semantics in JSON format
extracted from ECMAScript by {\sf Spec Extractor}.
